Classless Java

### 2015-10-01 paper/sections/Formalization.tex
mostSpecific
Added rule (Obj)
Ok, now shadow do the right thing.
It was easy, if there is a single method, that is the result,
if there are many methods, they must be all abstract, in that case take
the most specific, otherwise is a conflic and take the most specific as
a conflict
updated Context

\[
\inferrule{\textsf{mtype}(m,C) = \overline{D} \to E \\
\Gamma \vdash \overline{e} \in \overline{C} \\
\overline{C} <: \overline{D} \\
\textsf{mmodifier}(m,C) = \textbf{static} }
{\Gamma \vdash C.m(\overline{e}) \in E}
\quad \textsc{(T-StaticInvk)}
\]

\[
\inferrule{\textsf{mtype}(m,C) = \overline{D} \to E \\
\Gamma \vdash \overline{e} \in \overline{C} \\
\overline{C} <: \overline{D} \\
\textsf{checkSuper}(C.super.m(\overline{e}), A, C) \\\\
\text{\yanlin{check whether A <: C, where A is the enclosing interface of the
    expression}} }
{\Gamma \vdash C.\textbf{super}.m(\overline{e}) \in E}
\quad \textsc{(T-SuperInvk)}
\]

\subsubsection{Method Typing} 
\[ 
\inferrule 
{ }
{T_0 \spc m(\overline{T} \spc \overline{x}); \text{ OK IN I} }
\quad \textsc{(T-Meth)}
\]

@@

\subsubsection{Context}

\[ \Gamma = \epsilon \mid (x, C) : \Gamma  \]

@@

\[ \inferrule[(ReviewedRule)]{
  IT(C_0) = \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{
  \methods \} 
%\\
 % \methods(\m)=\method
%\\
%\Aux{tops}(\overline{C})=\C_1\ldots\C_n  
  }
{ \mBody(\m,\C_0) = \override(\methods(\m), %\shadow(\mBody(\m,C_1)\ldots\mBody(\m,C_n))
\shadow(\m,\Aux{tops}(\Cs)))
} \]
\subsubsection{Auxiliary function: $\tops(\Cs), \shadow(\m,\Cs),\override(\method,\method')$}

@@

\begin{equation*}
\begin{array}{ll}
\tops(\Cs)=\{\ \C\in\Cs\ |\ \nexists \C'\in\Cs\setminus\C,\ \C' \subtype \C\ \} 
\\
\shadow(\m,\C_1\ldots\C_n)=\shadow(\methods)
& \mBody(\m,\C_i)\in\methods
\\ & \mif\ \mBody(\m,\C)=\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}
\\ &\mor\ \mBody(\m,\C)=\mh\QM;
\\

\shadow()=\none\\
\shadow(\method)=\method\\
\shadow(\methods)=\conflicted\mh\QM;&\mif\ \Aux{mostSpecific}(\methods))\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}\}\\
\Aux{mostSpecific}(\methods)=\method &
\mif\ \method \in \methods, \forall \method' \in \methods :  \method' \subtype  \method,\\
\T\ \m\oR\T_1\x_1\ldots \T_n\x_n\cR \subtype \T' \m\oR\T_1\x_1'\ldots\T_n\x_n'\cR & \mif\ \T\subtype \T'\\

@@

@@

>>>>

\[
\inferrule{\textsf{mtype}(m,C) = \overline{D} \to E \\
\Gamma \vdash \overline{e} \in \overline{C} \\
\overline{C} <: \overline{D} \\
\textsf{mmodifier}(m,C) = \textbf{static} }
{\Gamma \vdash C.m(\overline{e}) \in E}
\quad \textsc{(T-StaticInvk)}
\]
\marco{rule tInvk must check is not static?}
\[
\inferrule{\textsf{mtype}(m,C) = \overline{D} \to E \\
\Gamma \vdash \overline{e} \in \overline{C} \\
\overline{C} <: \overline{D} \\
\textsf{checkSuper}(C.super.m(\overline{e}), A, C) \\\\
\text{\yanlin{check whether A <: C, where A is the enclosing interface of the
    expression}} }
{\Gamma \vdash C.\textbf{super}.m(\overline{e}) \in E}
\quad \textsc{(T-SuperInvk)}
\]

\[
\inferrule[(Obj)]{
\forall i\in 1\ldots n\ \Gamma,\Gamma^{\mh_i}\vdash\e_i\in \_\subtype\C^{\mh_i}\\
\forall\mh\in \mhs \mbox{ such that }
\mBody(\m^\mh,\C)=\method;\mh\subtype\mh^\method\\
\forall\m \mbox{ such that }
\mBody(\m,\C)\in\{\mh\QM;,\conflicted\mh\QM;\} \exists \mh_i \in\mhs\mbox{ such that }\mh_i\subtype\mh\\
\Gamma=\Gamma',\f_1{:}\T_1,\ldots,\f_k{:}\T_k,\,\QM{this}{:}\C\\
\mhs=\mh_1\ldots\mh_n
}{
\Gamma' \vdash\QM{new}\ \C\oR\cR\oC\T_1\ \f_1\QM;\ldots\T_k\ \f_k\QM;\
\mh_1\oC\QM{return}\ \e_1\QM{;}\!\cC
\ldots
\mh_n\oC\QM{return}\ \e_n\QM{;}\!\cC
\cC
\in\C
}
\]

\subsubsection{Method Typing}

\marco{I can not understand those rules, when is t-meth and t-meth body called? when is that you state that all methods in all interfaces must be ok?}
\[ 
\inferrule 
{ }
{T_0 \spc m(\overline{T} \spc \overline{x}); \text{ OK IN I} }
\quad \textsc{(T-Meth)}
\]

@@

\subsubsection{Context}
\[ \Gamma :: = \overline{x}:\overline{C} \]

The environment $\Gamma$ is a mapping from variables to types, written
$\overline{x}:\overline{C}$. Typing statement $\Gamma \vdash t:C$ reads ``in the
environment $\Gamma$, term $t$ has type $C$.'' We abbreviate typing statements on
sequences in a simple way, writing $\Gamma \vdash \overline{t}:\overline{C}$ as
shorthand for $\Gamma \vdash t_1:C_1,..., \Gamma \vdash t_n:C_n$.

@@

\[ \inferrule[(ReviewedRule)]{
  IT(C_0) = \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{
  \methods \} 
%\\
 % \methods(\m)=\method
%\\
%\Aux{tops}(\overline{C})=\C_1\ldots\C_n  
  }
{ \mBody(\m,\C_0) = \override(\methods(\m), %\shadow(\mBody(\m,C_1)\ldots\mBody(\m,C_n))
\shadow(\m,\Aux{tops}(\Cs)))
} \]
\subsubsection{Auxiliary function: $\tops(\Cs), \shadow(\m,\Cs),\override(\method,\method')$}
${}_{}$\\*
\marco{we need to discuss the names tops, shadow and override}

@@

\begin{equation*}
\begin{array}{ll}
\tops(\Cs)=\{\ \C\in\Cs\ |\ \nexists \C'\in\Cs\setminus\C,\ \C' \subtype \C\ \} 
\\
\shadow(\m,\C_1\ldots\C_n)=\shadow(\methods)
& \mBody(\m,\C_i)\in\methods
\\ & \mif\ \mBody(\m,\C)\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}\}
%\\ &\mor\ \mBody(\m,\C)=\mh\QM;
\\

\shadow()=\none\\
\shadow(\method)=\method\\
\shadow(\methods)=\Aux{mostSpecific}(\methods) &\mif\   \methods=\mh_1\QM;\ldots\mh_n\QM;\\
\shadow(\methods)=\conflicted\mh\QM;&\mif\ \Aux{mostSpecific}(\methods))\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}\}\\
\Aux{mostSpecific}(\methods)=\method &
\mif\ \method \in \methods, \forall \method' \in \methods :  \method \subtype
                                       \method', \\
\T\ \m\oR\T_1\x_1\ldots \T_n\x_n\cR \subtype \T' \m\oR\T_1\x_1'\ldots\T_n\x_n'\cR & \mif\ \T\subtype \T'\\

@@

%\text{\yanlin{shouldn't mostSpecific be: $\forall \method' \in \methods : \method \subtype
%  \method'$ ?}}

@@

%\marco{we also need to define a function that gives all the methods of an interface, something line}
%\[
%\Aux{methodsOf}_\C=\{\m|\mBody(\m,\C)=\method\}
%\]
